Trauma treatment delay

### 2023-12-12 manuscriptlongversion.Rmd
text

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes about 14,022 patients
treated between 2012 and 2022. The trauma care quality database is a
subset of the trauma registry and includes about 8000 patients selected
for review between 2013 and 2022. This project linked the two databases
and assessed how different patient level factors, such as age, sex,
blood pressure, and injury severity, are associated with delayed
treatment using logistic regression.

@@

The database only includes patients 15 years old and above, ISS \>9
and/or trauma team activation. Inclusion in the study further requires
that the patients have been assessed for OFIs. Patients were excluded if
they were missing information in one of the examined patient factors.

@@

The fact that age and gender did not show an increased odds ratio should
be seen as a positive sign. It suggests that among trauma patients,
there is no systematic delay based on gender or age.

@@

@@

@@

>>>>

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes 14,022 patients treated
between 2012 and 2022. The trauma care quality database is a subset of
the trauma registry and includes about 8000 patients selected for review
between 2013 and 2022. This project linked the two databases and
assessed how different patient level factors, such as age, sex, blood
pressure, and injury severity, are associated with delayed treatment
using logistic regression.

@@

The database only includes patients 15 years old and above, ISS \>9
and/or trauma team activation. Inclusion in the study further required
that the patients has been assessed for OFIs. Patients were excluded if
they were missing information in one of the examined patient factors.

@@

When looking at the patient demographic, it is clear that the majority
admitted to trauma care are men, with it being slightly higher in the
delay to treatment group. The fact that age and gender did not show an
increased odds ratio should be seen as a positive sign. It suggests that
among trauma patients, there is no systematic delay based on gender or
age.

#### Limitations

@@

#### Clinical applications

@@

#### Generalisability

@@

#### Future studies
